\documentclass{article}
\usepackage[a4paper,margin=2.5cm,nohead]{geometry}
\usepackage{enumerate}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{tabularx}
\usepackage{amsmath}
\usepackage[UTF-8]{inputenc}

\newenvironment{deflist}[1]{%
\begin{list}{}
{\renewcommand{\makelabel}[1]{\textbf{##1}\hfill}
\settowidth{\labelwidth}{\textbf{#1}}
\leftmargin=\labelwidth
\advance \leftmargin\labelsep}}
{\end{list}}
\newenvironment{optlist}[1]{%
\begin{list}{}
{\renewcommand{\makelabel}[1]{\texttt{##1}\hfill}
\settowidth{\labelwidth}{\texttt{#1}}
\leftmargin=\labelwidth
\advance \leftmargin\labelsep}}
{\end{list}}
\newenvironment{pullquote}{\begin{quotation}\Large}{\end{quotation}}
\setlength{\extrarowheight}{2pt}

\newcommand{\transition}{\begin{center}\rule{.8\textwidth}{0.2pt}\end{center}}
\newcommand{\subtitle}[1]{{\large\textsc{#1}}}
\newcommand{\subs}[1]{\raisebox{-0.7ex}{\footnotesize #1}}
\newcommand{\sups}[1]{\raisebox{0.7ex}{\footnotesize #1}}
\newcommand{\attribution}[1]{\raggedleft\textit{#1}}
\newcommand{\rubric}[1]{\vskip15pt{\large #1}}

\usepackage[pdftex]{hyperref}

\hypersetup{pdfcreator={VST, LaTeX, hyperref},
bookmarksopen=true,
bookmarksopenlevel=2,
colorlinks=true,urlcolor=blue,
}

\begin{document}
" Vim reStructured Text
" (c) Mikolaj Machowski 2006
" Author: Mikolaj Machowski ( mikmach AT wp DOT pl )
" Last Change: 30 Jun 2006
" Version: 1.1 Wedel
" License:
" Copyright (C) 2006 Mikolaj Machowski $<$mikmach@wp.pl$>$
"
" This script is free software; you can redistribute it and/or
" modify it under the terms of the GNU Library General Public
" License as published by the Free Software Foundation; either
" version 2 of the License, or (at your option) any later version.
"
" This library is distributed in the hope that it will be useful,
" but WITHOUT ANY WARRANTY; without even the implied warranty of
" MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE. See the GNU
" Library General Public License for more details.
"
" You should have received a copy of the GNU Library General Public License
" along with this library; see the file COPYING.LIB. If not, write to
" the Free Software Foundation, Inc., 51 Franklin Street, Fifth Floor,
" Boston, MA 02110-1301, USA.
" 
" VST requires Vim7
if v:version $<$ 700
 finish
endif

" Command :Vst
command! -range=\% -nargs=? -complete=custom,VST\_Args Vst call vst\#vst\#VST\_Export($<$line1$>$, $<$line2$>$, $<$q-args$>$)
command! -range=\% -nargs=? -complete=custom,VST\_Args Vsti call vst\#vst\#VST\_InstantWrapper($<$line1$>$, $<$line2$>$, $<$q-args$>$)
command! -range=\% -nargs=? -complete=custom,VST\_Args Vstm call VST\_Menus()

" VST\_Args: Command line completion for :Vst command \{\{\{function! VST\_Args(A, C, P)
 let args = "html,tex,latex,pdf,toc,head,fold,link,slink,rep,srep,preproc,help,rest"
 return substitute(args, ',', '$\backslash$n', 'g')
endfunction
" \}\}\}
" Menus \{\{\{function! VST\_Menus()
 if has("gui\_running")
 menu VreST.ExporttoHTML :Vst html$<$cr$>$
 menu VreST.Exportto\LaTeX{} :Vst tex$<$cr$>$
 menu VreST.ExporttoPDF :Vst pdf$<$cr$>$
 menu VreST.ExporttoreST :Vst rest$<$cr$>$
 menu VreST.Fold :Vst fold$<$cr$>$
 menu VreST.Headers :Vst head$<$cr$>$
 menu VreST.TOC :Vst toc$<$cr$>$
 menu VreST.Help :Vst help$<$cr$>$
 inoremenu VreST.ExporttoHTML $<$c-o$>$:Vst html$<$cr$>$
 inoremenu VreST.Exportto\LaTeX{} $<$c-o$>$:Vst tex$<$cr$>$
 inoremenu VreST.ExporttoPDF $<$c-o$>$:Vst pdf$<$cr$>$
 inoremenu VreST.ExporttoreST $<$c-o$>$:Vst rest$<$cr$>$
 inoremenu VreST.Fold $<$c-o$>$:Vst fold$<$cr$>$
 inoremenu VreST.Headers $<$c-o$>$:Vst head$<$cr$>$
 inoremenu VreST.TOC $<$c-o$>$:Vst toc$<$cr$>$
 inoremenu VreST.Help $<$c-o$>$:Vst help$<$cr$>$
 endif
endfunction
if exists("g:vst\_showmenu") \&\& g:vst\_load\_menus != 0
 call VST\_Menus()
endif
" \}\}\}
\end{document}

